Assessing Ranking Fidelity of Competition Structures via Weighted Mutual Information

### 2025-10-22 CMSAC_presentation/CMSAC_reveal_js.qmd

    - A good tournament: top *k* produced by the tournament matches closely to the true top *k*

-   **Efficacy**[^1]: Final rankings should match the true rankings of the strength of the competitors

-   **Effectivity**[^2]: Interested in correctly ranking the best competitor as first

[^1]: Lasek and Gagolewsk (2018), Sziklai, Biró, and Csató (2022)

[^2]: Glenn (1960)

@@

::: {.fragment}
-   **Salient ranks**: output ranks of the competition you want to get correct
    -   Effectivity: 1 is only salient rank
    -   Efficacy: 1 through $n$ are salient ranks
:::

@@

-   Want to quantify how well a structure can accurately order the competitors
-   We propose a metric that quantifies how effectively different competition structures recover the true ranking

>>>>

    - A good tournament: top *k* teams produced by the tournament matches closely to the true top *k*

-   **Effectivity**[^1]: Interested in correctly ranking the best competitor as first

-   **Efficacy**[^2]: Final rankings should match the true rankings of all the competitors

[^1]: Glenn (1960)

[^2]: Lasek and Gagolewsk (2018), Sziklai, Biró, and Csató (2022)

@@

::: {.fragment}
-   **Salient ranks**: output ranks of the competition you want to get correct
    -   Effectivity: 1 is only salient rank
    -   Efficacy: 1 through $n$ are salient ranks
=======
-   **Salient ranks**: output ranks of the tournament you want to get correct
    -   Effectivity: 1 is only salient rank (*k*=1)
    -   Efficacy: 1 through $n$ are salient ranks (*k*=n)
:::

@@

-   Want to quantify how well a structure can accurately order the competitors
-   We propose a metric that quantifies how effectively different competition structures recover the true ranking
=======
-   Quantify how well a structure can accurately order the competitors using weighted mutual information
-   We propose a metric that quantifies how effectively different tournament structures recover the true ranking of the teams
